Preregistration analysis, Cost 2 study

### 2019-08-02 Cost2/Cost2_prereg.Rmd
corrected error miscalculating the p(AR_effects) in Cost 3, plus better matching of htmls

``` {r Load Data, echo=FALSE}
### data loading and cleaning up
# recent addition: turning forced travels to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
setwd("./data")
files <- dir(pattern = '_log.csv')
nSubjs <- length(files)

@@

# get a simple subject list and the number of subjects
subjList <- unique(dataAll$SubjID)
nSubj <- length(subjList)

@@

# Around 10% seemed to have been influenced by previous quitting
prcntAR_effects <- mean(AR_CIs) * 100
```

To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero. By this measure, around `r round(prcntAR_effects)` percent of our participants seemed to have been influenced by recent quitting. However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.

>>>>

``` {r Load Data, echo=FALSE}
### data loading and cleaning up
# recent addition: turning forced travels to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
# NOTE: P389 IS DUPLICATED. FIND OUT REAL ID # FOR ONE OF THEM.
setwd("./data")
files <- dir(pattern = '_log.csv')

@@

# get a simple subject list and the number of subjects
subjList <- unique(dataAll$SubjID)
nSubjs <- length(subjList)

@@

To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero. By this measure, `r sum(AR_CIs)` out of `r nSubjs` of our participants seemed to have been influenced by recent quitting. However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.
